\documentclass{exam}

\usepackage[margin=1.0in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{csquotes}
\usepackage{t1enc}
\usepackage[english]{babel}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{changepage}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{xcolor}
\usepackage[
    backend=biber,
    style=ieee
]{biblatex}
\usepackage[pdfusetitle]{hyperref}
\usepackage{graphicx}
\graphicspath{ {./img/} }
\usepackage{siunitx}
\hypersetup{pdftex,colorlinks=true,allcolors=black}

\pagestyle{headandfoot}
\firstpageheader{Kotlin for Android Development}{}{}
\runningheader{}{}{}
\firstpagefooter{}{}{}
\runningheadrule

\begin{document}
\title{Kotlin for Android Development Assignment Specification}
\author{Daniel Meszaros (JHZF2T)}
\date{2020/21/1}
%\maketitle

\emph{Surveyor} is a GPS track recorder application that makes it
possible to save and share hiking routes.

Users can \textbf{review these recordings}, overlaying them on an interactive
map, and even \textbf{export them} as \textbf{standard GPX files} for
interchange with other devices and software.
\textbf{Saved recordings can be given a custom title}, so that the users may
find them more quickly when searching.

The \textbf{built-in map} can be used for navigation even while the user is currently
recording a route, with the recorded data being overlayed onto the map and
updated in real-time.
A \textbf{compass arrow} is drawn at user's location indicating the direction
they face.

Since there is no way to charge the phone on the trail (aside from external
battery packs) the application should be power efficient and not waste energy.
Alternative trackers like \emph{OSMtracker} and \emph{ViewRanger} stop recording
any location data when the screen is locked.
This means that the user needs to keep the screen on, which quickly drains the
battery.
An important feature of this application that \textbf{it works even when it's
in the background}.

Users can \textbf{mark points-of-interest} with the press of a button. These
markers/waypoints are stored in the recording as well.

The application can generate \textbf{speed and elevation graphs}, as well as
\textbf{statistical information} like average speed, top speed, etc. when
reviewing a past recording.

The user are not required to login or be online to record routes, but
downloading maps still need an internet connection.

I intend to use the OpenStreetMaps Android
library\footnote{https://github.com/osmdroid/osmdroid} as it's much more
detailed when it comes navigation on hiking trails and it supports drawing lines
on the map.

\end{document}
